%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {Traverse Technologies} % Organization
  {Singapore} % Location
  {Jun 2020 - present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Basis AI} % Organization
  {Singapore} % Location
  {May 2019 - Jun 2019; Sep 2019 - Apr 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Helped built the company's MVP web app using aiohttp in Python for backend, as well as React, Redux, and Typescript for frontend.}
    \item {Also interfaced with infrastructure tools such as Kubernetes and Helm.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Quantitative Research Intern} % Job title
  {Jump Trading LLC} % Organization
  {Singapore} % Location
  {Jun 2018 - Aug 2018; Jul 2019 - Aug 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    % \item {Learnt basic finance and trading skills, such as: market-making, passive/aggressive orders, momentum follow, mean inversion.}
    \item {Compared different machine learning models: linear regression (with regularization), random forests, gradient boosted regression trees (GBRT), and recurrent neural networks (RNN), on financial market data.}
    \item {Researched and simulated the impact of trading signals for various markets.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Bloomberg LP} % Organization
  {London} % Location
  {Aug 2018 - Dec 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Added a scalable backpressure system for the C++ core infrastructure that supports providing live financial data to all clients, involving various internal tools and well-known tools such as Redis.}
    \item {Implemented many command-line scripts in Python to automate internal tasks.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Data Science Intern} % Job title
  {Twitter Inc.} % Organization
  {Singapore} % Location
  {May 2017 - Aug 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented complex Scalding (MapReduce) jobs to categorize data of traffic coming to Twitter, splitting them based on various variables.}
    \item {Presented visualizations of these datasets (in Tableau) to the whole data science team as well as to marketing teams.}
    % \item {Analyzed and presented data of Twitter emails. The data was used to inform a product manager on traffic-driving emails.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Sea Ltd.} % Organization
  {Singapore} % Location
  {May 2016 - Aug 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Established a data aggregation system for Garena's real-time data to reduce time and memory usage of users' queries.}
    \item {Developed an API to assist programmers in obtaining results from the data aggregation system.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
